### 2018-05-15 Paper/examples.tex
..

Our goal as discussed is to gain computational advantage by constructing
surrogates in a reduced input parameter space. To this end, we construct PCE's
in 5D and 4D spaces by fixing $\{T_u,T_l\}$ in the former and additionally
fixing $K_w$ in the latter at their respective mean values. In
Figure~\ref{fig:conv_bore}(left), we compare convergence of PCE's constructed in the
full space (7D) with those constructed in the two reduced spaces (4D and 5D)
using $\epsilon_{\mbox{\tiny{LOO}}}$ (Eq.~\ref{eq:loo}). 
\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.48\textwidth]{./Figures/err_samples_borehole}
  \includegraphics[width=0.48\textwidth]{./Figures/pdf_comp_borehole}
\caption{Left: A comparison of order of the leave-one-out-error 
($\epsilon_{\mbox{\tiny{LOO}}}$) as a function of number of regression samples
used for constructing the PCE in 4, 5, and 7 dimensions. Right: A comparison of
PDFs of the discharge, $\mathcal{Q}$, generated using 10$^{6}$ samples from
the marginal distributions of the uncertain parameters in each case.} 
\label{fig:conv_bore}
\end{center}
\end{figure}

As expected, it is observed that the PCE constructed in the 4D space converges
at a much faster rate. For instance, if a PCE with $\mathcal{O}(10^{-4})$
accuracy is sought, we need function evaluations at only about 50 sample points
in the 4D parameter space whereas the number of samples needed in the full 7D
space seems much higher.~\alennote{How are these samples used? Are we doing 
Latin Hypercube sample, or some other QMC approach?}

@@

Figure~\ref{fig:conv_bore}(right) illustrates a comparison of the PDFs
of the
discharge, $\mathcal{Q}$ obtained by propagating 10$^6$ random
samples through the 7D PCE in the original input parameter domain as well as
the reduced order PCEs constructed in 4 and 5 dimensions. 
%\begin{figure}[htbp]
% \begin{center}
%  \includegraphics[width=0.6\textwidth]{./Figures/pdf_comp_borehole}
%\caption{A comparison of PDF's of the discharge, $\mathcal{Q}$ as obtained
%by propagating
%parametric uncertainties through the 4D, 5D, and 7D PCE's.These PDF's 
%were obtained using 10$^{6}$ MC samples in the input parameter domain.} 
%\label{fig:pdfcomp_bore}
%\end{center}
%\end{figure}
It is evident from this plot, that the PDFs agree quite favorably with each
other with respect to the modal estimate as well as the uncertainty associated with 
$\mathcal{Q}$. 
Consequently, it can be said that the reduced order PCE is verified in a
probabilistic sense. In other words, the mode as well as the uncertainty in the
observable is reliably captured and predicted by the reduced order PCE.

>>>>

Our goal as discussed is to gain computational advantage by constructing
surrogates in a reduced input parameter space. To this end, we use LAR to 
construct PCEs
in 5D and 4D spaces by fixing $\{T_u,T_l\}$ in the former and additionally
fixing $K_w$ in the latter at their respective mean values. In
Figure~\ref{fig:conv_bore}(left), we compare convergence of PCEs constructed in the
full space (7D) with those constructed in the two reduced spaces (4D and 5D)
using $\epsilon_{\mbox{\tiny{LOO}}}$ (Eq.~\ref{eq:loo}).

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.48\textwidth]{./Figures/err_samples_borehole}
  \includegraphics[width=0.48\textwidth]{./Figures/pdf_comp_borehole}
\caption{Left: A comparison of order of the leave-one-out-error 
($\epsilon_{\mbox{\tiny{LOO}}}$) as a function of number of regression samples
used for constructing the PCE in 4, 5, and 7 dimensions. Right: A comparison of
PDFs of the discharge, $\mathcal{Q}$, generated using 10$^{6}$ samples from
the marginal distributions of the uncertain parameters in each case.} 
\label{fig:conv_bore}
\end{center}
\end{figure}

As expected, it is observed that the PCE constructed in the 4D space converges
at a much faster rate. For instance, if a PCE with $\mathcal{O}(10^{-4})$
accuracy is sought, we need function evaluations at only about 50 sample points
in the 4D parameter space whereas the number of samples needed in the full 7D
space seems much higher. Latin hypercube sampling (LHS) was used in
each case. It must be pointed out that the error in Figure~\ref{fig:conv_bore}(left)
is not expected to decrease monotonically with the increase in sample size
owing to the penalty term in the regularized optimization problem in Eq.~\ref{eq:reg}.

@@

Figure~\ref{fig:conv_bore}(right) illustrates a comparison of the PDFs
of the
discharge, $\mathcal{Q}$ obtained by propagating 10$^6$ random
samples through the 7D PCE in the original input parameter domain as well as
the reduced order PCEs constructed in 4 and 5 dimensions. 
It is evident from this plot, that the PDFs agree quite favorably with each
other with respect to the modal estimate as well as the uncertainty associated with 
$\mathcal{Q}$. 
Consequently, it can be said that the reduced order PCE is verified in a
probabilistic sense. In other words, the mode as well as the uncertainty in the
observable is reliably captured and predicted by the reduced order PCE.
